Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
no more stable

# Results
Individuals in multilayer networks became more connected as the spatial distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which graph strength stabilized. GPS
data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
confirm the use of 50 m buffer that has long been used for studies in the field
[@Lingle_2003; @Clutton_1982]

>>>>

# Results
Individuals in multilayer networks became more connected as the spatial distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
confirm the use of 50 m buffer that has long been used for studies in the field
[@Lingle_2003; @Clutton_1982]
